---
title: "Using `epiVN`"
author: "Marc Choisy"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using epiVN}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r include = FALSE}
knitr::knit_hooks$set(margin = function(before, options, envir) {
  if (before) par(mgp = c(1.5, .5, 0), bty = "n", plt = c(.105, .97, .13, .97))
  else NULL
})

knitr::opts_chunk$set(margin = TRUE, prompt = TRUE, comment = "",
                      collapse = TRUE, cache = FALSE,
                      dev.args = list(pointsize = 11), fig.height = 3.5,
                      fig.width = 4.24725, fig.retina = 2, fig.align = "center")
```

This package contains vaccine coverages by province and year in Vietnam. These
data come from the WHO's *Expanded Programme on Immunization* (EPI).

## Installation and loading

You can install `epiVN` from [GitHub](https://github.com/choisy/epiVN)

```{r eval = FALSE}
# install.packages("devtools")
devtools::install_bitbucket("choisy/epiVN", build_vignettes = TRUE)
```

Once installed, you can load the package:

```{r}
library(epiVN)
```

## Usage examples

So far, there is vaccination data only against **Japanese encephalitis**, per
province, per year from 1997 to 2016. These data are contained in the `je` data
frame. Data against other diseases will be added latter on.

```{r}
data(je)
dim(je)
head(je)
```

The data are defined for a given province (`province`), a given year (`year`),
and a given vaccination dose scheme (`nb_doses`) and contains:

* `nb_districts`: the number of districts where the vaccine policy is implemented;

* `districts_tot`: the total number of districts in the given province for the
given year (varies from province to province but also potentially from year to year);

* `nb_people`: the number of people that have been vaccinated;

* `people_tg`: the targetted number of people to vaccinate.

Note that the `nb_districts` is the same for the 2 doses scheme of a given
province and a given year.


### Percentage of districts included in the programme as a function of time

The number of districts included in the vaccination programme increases with
time:

```{r}
plot(nb_districts / districts_tot ~ year, subset(je, nb_doses == 2),
     pch = 19, col = rgb(0, 0, 0, .1),
     xlab = NA, ylab = "percentage of districts")
```

### Vaccine coverages

```{r}
with(je, hist(nb_people / people_tg, n = 20, col = "grey",
              xlab = "vaccine coverage", ylab = "frequency"))
```



